Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda

### 2013-04-29 Web3D2013-Dec3D/paper.tex
added v-must

\author{
Jacek Jankowski\thanks{e-mail:jacek.jankowski@inria.fr} \\ Inria \\ Bordeaux \\ France
\and Sandy Ressler\thanks{e-mail:sandynist@gmail.com} \\ NIST \\ Gaithersburg MD \\ USA
\and Kristian Sons\thanks{e-mail:kristian.sons@dfki.de} \\ DFKI \\ Saarbr\"ucken \\ Germany
\and Yvonne Jung\thanks{e-mail:yvonne.jung@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Johannes Behr\thanks{e-mail:johannes.behr@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Philipp Slusallek\thanks{e-mail:slusallek@cs.uni-saarland.de} \\ DFKI \& Saarland University \\ Saarbr\"ucken \\ Germany
}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\columnwidth]{images/Dec3D-Architecture.png}
  \caption{Proposed Declarative 3D ``Polyfill'' Runtime Architecture.}
  \label{fig:polyArch}
  %\vspace{-0.2cm}
\end{figure}

@@

\section*{Acknowledgements}
The research presented in this paper has been supported by the EU projects VERVE\footnote{http://www.verveconsortium.eu/} and FI-CONTENT, the BMBF project EMERGENT, the Intel Visual Computing Institute, the SFI's Lion2 and EI's Copernicus projects, and the Villes Transparentes project.

>>>>

\author{
Jacek Jankowski\thanks{e-mail:jacek.jankowski@inria.fr} \\ Inria \\ Bordeaux \\ France
\and Sandy Ressler\thanks{e-mail:sressler@acm.org} \\ NIST \\ Gaithersburg MD \\ USA
\and Kristian Sons\thanks{e-mail:kristian.sons@dfki.de} \\ DFKI \\ Saarbr\"ucken \\ Germany
\and Yvonne Jung\thanks{e-mail:yvonne.jung@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Johannes Behr\thanks{e-mail:johannes.behr@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Philipp Slusallek\thanks{e-mail:slusallek@cs.uni-saarland.de} \\ DFKI \& Saarland University \\ Saarbr\"ucken \\ Germany
}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\columnwidth]{images/Dec3D-Architecture.png}
  \caption{The proposed Declarative 3D ``Polyfill'' Runtime Architecture.}
  \label{fig:polyArch}
  %\vspace{-0.2cm}
\end{figure}

@@

\section*{Acknowledgements}
The research presented in this paper has been supported by the EU projects V-Must (\url{http://v-must.net}), VERVE (\url{http://www.verveconsortium.eu}) and FI-CONTENT, the BMBF project EMERGENT, the Intel Visual Computing Institute, the SFI's Lion2 and EI's Copernicus projects, and the Villes Transparentes project.
